---
title: "Final Project"
author: "abcd"
date: "today"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(countrycode)
```


```{r}
salaries = read.csv("ds_salaries.csv")
```

#Top 5 jobs each year get best pay
```{r}
salaries %>%  group_by(work_year,job_title) %>% summarise(avg_salary = mean(salary_in_usd)) %>%  slice_max(avg_salary, n=3)
```

Average salary each job get 2020-2022
```{r}
salaries %>% group_by(job_title) %>% summarise(avg_salary = mean(salary_in_usd))
```

Average salary in each "job", "Size_company" pay 2020-2022
```{r}
salaries %>% group_by(company_size,job_title) %>% summarise(avg_salary = mean(salary_in_usd))
```



#Top 3 jobs most appear
```{r}
salaries %>% group_by(job_title) %>% count() %>% arrange(desc(n)) %>% head(3)
```

##Compare salary each "size_company" pay for of top 3 job_title (bargraph)
```{r}
# I want to find the jobtitle that all hired on all comp_size, is there any way to get it.

salaries %>% filter(job_title %in% c("Data Scientist", "Data Engineer","Data Analyst")) %>%  group_by(company_size,job_title) %>% summarise(avg_salary = mean(salary_in_usd))
```

#Salary between working remote and onshore => color by company_size


#Total company in size for remote-working


#% remote among L,M,S company_size
#% exp_level maong LMS company_size

# avg salry all over the world (an diem,worldmap)
```{r}
country = salaries$employee_residence

salaries$country = countrycode(country, "iso2c", "country.name")

salaries %>% group_by(country) %>% summarise(avg_salary = mean(salary_in_usd))
#phai hon 5 thang cua 1 nuoc moi bo vao data
```

# Total of job_title per country  over the world (???)
```{r}
country = salaries$employee_residence

salaries$country = countrycode(country, "iso2c", "country.name")

salaries %>% group_by(country,job_title) %>% count() %>% arrange(desc(n))

```


#Which country hire people most


#the involution of exp_level via each year by salary (line graph, y = sal, x = year, color = exp_level)
```{r}
test = salaries %>% group_by(work_year,experience_level) %>% summarize(avg_salary = mean(salary))

ggplot(test, aes(x = work_year, y = avg_salary,color = experience_level))+ geom_line()
```
##I have no idea if company decrease man-power, increase salary