---
title: "Final Project"
author: "abcd"
date: "today"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(countrycode)
library(ggthemes)
require(maps)
require(viridis)
```


```{r}
salaries = read.csv("ds_salaries.csv")
```

#Top 5 jobs each year get best pay
```{r}
salaries %>%  group_by(work_year,job_title) %>% summarise(avg_salary = mean(salary_in_usd)) %>%  slice_max(avg_salary, n=3)
```

Average salary each job get 2020-2022
```{r}
salaries %>% group_by(job_title) %>% summarise(avg_salary = mean(salary_in_usd))
```

Average salary in each "job", "Size_company" pay 2020-2022
```{r}
salaries %>% group_by(company_size,job_title) %>% summarise(avg_salary = mean(salary_in_usd))
```



#Top 3 jobs most appear
```{r}
salaries %>% group_by(job_title) %>% count() %>% arrange(desc(n)) %>% head(3)
```

##Compare salary each "size_company" pay for of top 3 job_title (bargraph)
```{r}
# I want to find the jobtitle that all hired on all comp_size, is there any way to get it.

salaries %>% filter(job_title %in% c("Data Scientist", "Data Engineer","Data Analyst")) %>%  group_by(company_size,job_title) %>% summarise(avg_salary = mean(salary_in_usd))
```


# avg salry all over the world (an diem,worldmap)
```{r}
country_employee = salaries$employee_residence

salaries$country_employee = countrycode(country_employee, "iso2c", "country.name")

salaries %>% group_by(country_employee) %>% summarise(avg_salary = mean(salary_in_usd))

```

```{r}
world_map <- map_data("world")
world_salaries <-salaries %>% group_by(country_employee) %>% summarise(avg_salary = mean(salary_in_usd))

# Changing the data manaually so that it matches

setdiff(world_salaries$country_employee, world_map$region)

world_salaries[world_salaries == "United States"] <- "USA"
world_salaries[world_salaries == "Czechia"] <- "Czech Republic"
#world_salaries[world_salaries == "Hong Kong SAR China"] <- "China"
world_salaries[world_salaries == "United Kingdom"] <- "UK"

countries_map <- right_join(world_salaries, world_map, by = c("country_employee"="region"))

ggplot(countries_map, aes(long, lat, group = group))+
  geom_polygon(aes(fill = avg_salary ), color = "white")+ scale_fill_viridis_c(option = "B")
```

#ratio between company_size with remote_ratio
```{r}
salaries$remote_ratio[salaries$remote_ratio == '100'] <- '100%'
salaries$remote_ratio[salaries$remote_ratio == '50'] <- '50%'
salaries$remote_ratio[salaries$remote_ratio == '0'] <- '0%'

ggplot(salaries %>% group_by(company_size, remote_ratio)) + 
  geom_bar(mapping = aes(x = company_size, fill = remote_ratio), position = "dodge")

```


# Compare on-shore and remote salary
```{r}
#salary_explevel = salaries %>% group_by(work_year, remote_ratio) %>% summarize(avg_salary = mean(salary))
#ggplot(salary_explevel, aes(x = work_year, y = avg_salary,color = remote_ratio))+ geom_density()

ggplot(salaries %>% group_by(company_size, remote_ratio)) + 
  geom_bar(mapping = aes(x = company_size, fill = remote_ratio), position = "dodge")

ggplot(salaries) + geom_bar(mapping = aes(x = remote_ratio, fill = remote_ratio))

```


#Which country hire people most


#the involution of exp_level via each year by salary (line graph, y = sal, x = year, color = exp_level)
```{r}
salary_explevel = salaries %>% group_by(work_year,experience_level) %>% summarize(avg_salary = mean(salary))

ggplot(salary_explevel, aes(x = work_year, y = avg_salary,color = experience_level))+ geom_line()
```
##I have no idea if company decrease man-power, increase salary